---
title: "Preliminary Text-Analyses"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file='index.html')})
author: "Cristian Rodriguez"
date: "8/8/2019"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
load("Output.Rdata")
load("Huge.Rdata")
library(ggcorrplot)
library(reshape)
library(MASS)
library(tidyverse)
library(knitr)
library(rmarkdown)
library(psych)
library(kableExtra)
opts_chunk$set(results = 'asis',      # This is essential (can also be set at the chunk-level)
                comment = NA, 
                prompt = FALSE, 
                cache = FALSE)

library(summarytools)
st_options(plain.ascii = FALSE,style = "rmarkdown",footnote = NA,subtitle.emphasis = FALSE)
st_css()


```
# Data Structuring
The transcriptions were processed by separating each line of text, labeling pair, participant, topic, extension and medium. Different data structures were produced (word-level, intervention-level, person-level, pair-level, condition-level). For these results, all participant interventions were grouped and analyzed with the `liwc_alike()` function of the `quanteda` package. The word categories are identical to those from the LIWC software. Additionally, output scores (how responsive was your partner, how conflicted was the conversation, "how much mind" does your partner have) were appended for each participant, as well as the scores given by the conversation partner. Variables labeled as `alt_` indicate partner perception.

# Descriptives
```{r general_descriptives, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
  
dfSummary(Output[,c(2,3,6:8, 12:14, 21, 42, 48, 53, 60, 64, 69, 78, 88)], round.digits = 2, valid.col = FALSE, headings = FALSE, na.col = FALSE, graph.magnif = .75, style = "grid", tmp.img.dir = "/tmp", silent = T)

```

## By Medium
``` {r descriptives,  echo=FALSE, error=FALSE, message=FALSE, warning=FALSE }

Vars<-c("Mind - attributed by partner", "Conflict - attributed by partner", "Responsiveness - attributed by partner", "Function words", " Affective words", "Social words","Cognitive words", " Perceptual words", "Biological words", "Drive-related words" , "Relative words (space, time)", "Informal language")

Output[,c(2,6:8, 12:14, 21, 42, 48, 53, 60, 64, 69, 78, 88)] %>%
  group_by(Medium) %>%
  summarize(Mind = mean(alt_Dehum), Conflict = mean(alt_Conf), Responsiveness = mean(alt_Resp), Function = mean(function..function.words.), 
            Affective = mean(affect..affect.), Social = mean(social..social.), Cognitive = mean(cogproc..cognitive.processes.),
            Perceptual = mean(percept..perceptual.processes.), 
            Biological = mean(bio..biological.processes.), 
            Drives = mean(drives..drives.), Orientation = mean(relativ..relativity.), 
            Informal = mean(informal..informal.language.))%>%
  kable( digits = 2, align = "c",caption = "Word categories by Medium") %>%
  kable_styling(full_width = TRUE)
  
Output[,c(1,2,21, 42, 48, 53, 60, 64, 69, 78, 88)] %>%
  melt(id.vars = 1:2, measure.vars = 3:11 ) %>%
  ggplot(aes(reorder(variable, value), value, fill = Medium)) + 
  stat_summary(geom = "col",position = "dodge2") + 
  stat_summary(geom = "errorbar", position = "dodge2") + 
  coord_flip() + labs(y = "Proportion", x = "LIWC term categories", title = "Term Frequency, by Medium",
                      caption = "n = 406") +
  scale_x_discrete(labels = rev(c("Function words","Cognitive ('know', 'should', 'think)", 
                                  "Social ('mate', 'talk', 'they')",
                                  "Movement ('go', 'end', 'in')",
                                  "Drives (affiliation, power, etc.)",
                                  "Affect ('happy', 'cry', 'sweet')",
                                  "Informal (fillers, swear, etc.)",
                                  "Perceptual ('see', 'hear', 'feel')",
                                  "Biological ('eat', 'blood', 'pain')")))

Results<-data.frame( "Variable" = Vars,
                     "t-stat" = vector( mode = "numeric", length = 12),
                     "p-value" = vector( mode = "numeric", length = 12),
                     "LL" = vector( mode = "numeric", length = 12),
                     "UL" = vector( mode = "numeric", length = 12),
                     "Cohens D" = vector( mode = "numeric", length = 12), 
                     stringsAsFactors = FALSE)

for (i in 1:12) {
  num<-c(12:14,21, 42, 48, 53, 60, 64, 69, 78, 88)[i]
  names(Output)[num]-> name
  res<-t.test(data=Output,    Output[,name] ~ as.factor(Output$Medium) )
  Results[i,2]<-as.numeric(res$statistic)
  Results[i,3]<-as.numeric(res$p.value)
  Results[i,4:5]<-as.numeric(res$conf.int)
  Results[i,6]<-t2d(Results[i,2],  nrow(Output))
}
  
Results %>%
  mutate(Sig  = if_else(p.value < .001, "***", 
                       if_else(p.value <= .01, "**", 
                               if_else(p.value <= .05, "*", "")))) %>%
kable(digits = 3, caption = "Audio minus Text (Negative estimates indicate higher values for Text)") %>%
  kable_styling(full_width = TRUE)

```


**Comments**:  Higher mind (*t* =`r round(Results[1,2],2)`,*d* = `r round( Results[1,6],2)` and responsiveness  (*t* =`r round(Results[3,2], 3)`,*d* = `r round(Results[3,6],2)`) attributed by partner in Audio over Text, but no differences in Conflict. Informal language is higher (*t* =`r round(Results[12,2],2)`,*d* = `r round( Results[12,6],2)`) in Audio, whereas words related to affect (*t* =`r round(Results[5,2],2)`,*d* = `r round( Results[5,6],2)`), social relations (*t* =`r round(Results[6,2],2)`,*d* = `r round( Results[6,6],2)`), biological processes (*t* =`r round(Results[9,2],2)`,*d* = `r round( Results[9,6],2)`)and drives (affiliation, power, etc.; *t* =`r round(Results[10,2],2)`,*d* = `r round( Results[10,6],2)`) are more predominant in Text-based conversations.


## By Condition

``` {r descriptives2,  echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

Output[,c(3,6:8, 12:14, 21, 42, 48, 53, 60, 64, 69, 78, 88)] %>%
  group_by(Extension) %>%
  summarize(Mind = mean(alt_Dehum), Conflict = mean(alt_Conf), Responsiveness = mean(alt_Resp), Function = mean(function..function.words.), 
            Affective = mean(affect..affect.), Social = mean(social..social.), Cognitive = mean(cogproc..cognitive.processes.),
            Perceptual = mean(percept..perceptual.processes.), 
            Biological = mean(bio..biological.processes.), 
            Drives = mean(drives..drives.), Orientation = mean(relativ..relativity.), 
            Informal = mean(informal..informal.language.))%>%
  kable( digits = 2, align = "c",caption = "Word categories by Extension") %>% 
  kable_styling(full_width = TRUE)


Output[,c(1,3,21, 42, 48, 53, 60, 64, 69, 78, 88)] %>%
  melt(id.vars = 1:2, measure.vars = 3:11 ) %>%
  ggplot(aes(reorder(variable, value), value, fill = Extension)) + 
  stat_summary(geom = "col",position = "dodge2") + 
  stat_summary(geom = "errorbar", position = "dodge2") + 
  coord_flip() + labs(y = "Proportion", x = "LIWC term categories", title = "Term Frequency, by Extension",
                      caption = "n = 406") +
  scale_x_discrete(labels = rev(c("Function words","Cognitive ('know', 'should', 'think)", 
                                  "Social ('mate', 'talk', 'they')",
                                  "Movement ('go', 'end', 'in')",
                                  "Drives (affiliation, power, etc.)",
                                  "Affect ('happy', 'cry', 'sweet')",
                                  "Informal (fillers, swear, etc.)",
                                  "Perceptual ('see', 'hear', 'feel')",
                                  "Biological ('eat', 'blood', 'pain')")))


for (i in 1:12) {
  num<-c(12:14,21, 42, 48, 53, 60, 64, 69, 78, 88)[i]
  names(Output)[num]-> name
  res<-t.test(data=Output,    Output[,name] ~ as.factor(Output$Extension) )
  Results[i,2]<-as.numeric(res$statistic)
  Results[i,3]<-as.numeric(res$p.value)
  Results[i,4:5]<-as.numeric(res$conf.int)
  Results[i,6]<-t2d(Results[i,2],  nrow(Output))
}
  
Results %>%
  mutate(Sig  = if_else(p.value < .001, "***", 
                       if_else(p.value <= .01, "**", 
                               if_else(p.value <= .05, "*", "")))) %>%
kable(digits = 3, caption = "Long minus Short  (Negative estimates indicate higher values for Short)") %>% 
  kable_styling(full_width = TRUE)

```



**Comments**: There are basically no significant differences among outcomes or language use between Short and Long conditions. 

# Analyses

## Correlations

```{r correlations, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.align="center", fig.dim=c(10,12), fig.cap="NOTE: blank spaces are non-significant correlations"}
library(ggcorrplot)

mat<-round(cor(Output[,c(6:8, 12:14, 21, 42, 48, 53, 60, 64, 69, 78, 88)], ),3)
pmat<-corr.p(mat, n= nrow(Output))
ggcorrplot(mat, type = "lower", hc.order = FALSE, p.mat = pmat$p, lab = TRUE, insig = "blank", lab_size = 4) + 
  labs(caption = "Zero-order correlations")
```

**Comments**: Responsiveness, Conflict and Mind perceived by partner (`alt_Resp`, `alt_Conf`, and `alt_Dehum` respectively) are negatively associated with words related to Social relations, Biological Processes and Drives (positively for conflict); yet, positively associated with Informal language. Also perceived Conflict is associated with less affective words and more cognitive words.

## Linear Plots

These plots represent the linear relationship of each word category with all three outcomes. Datapoints were not plotted to avoid getting messy plots. 
``` {r plots, echo=FALSE, error = FALSE, message= FALSE, warning=FALSE,fig.align="center", fig.dim=c(12,12)}
## Barplot: 3 outcomes, by categories 
# Affective terms
A<-ggplot(Output) + 
  #geom_point(aes(affect..affect.,alt_Dehum)) + 
  geom_smooth(aes(affect..affect.,alt_Dehum, color = "red"), method = "lm") +
  #geom_point(aes(affect..affect.,alt_Conf)) + 
  geom_smooth(aes(affect..affect.,alt_Conf, color = "green"), method = "lm") +  
  #geom_point(aes(affect..affect.,alt_Resp)) + 
  geom_smooth(aes(affect..affect.,alt_Resp, color = "blue"), method = "lm") +
  scale_color_discrete(name = "Attributed", labels = c("Dehumanization", "Conflictive", "Responsiveness")) +
  labs(title = "Affective terms",x = "Proportion", y = "Partner attributions")

# Function words
B<-ggplot(Output) + 
  #geom_point(aes(function..function.words.,alt_Dehum)) + 
  geom_smooth(aes(function..function.words.,alt_Dehum, color = "red"), method = "lm") +
  #geom_point(aes(function..function.words.,alt_Conf)) + 
  geom_smooth(aes(function..function.words.,alt_Conf, color = "green"), method = "lm") +  
  #geom_point(aes(function..function.words.,alt_Resp)) + 
  geom_smooth(aes(function..function.words.,alt_Resp, color = "blue"), method = "lm") +
  scale_color_discrete(name = "Attributed", labels = c("Dehumanization", "Conflictive", "Responsiveness")) +
  labs(title = "Function Words",x = "Proportion", y = "Partner attributions")

# Social terms
C<-ggplot(Output) + 
  #geom_point(aes(social..social.,alt_Dehum)) + 
  geom_smooth(aes(social..social.,alt_Dehum, color = "red"), method = "lm") +
  #geom_point(aes(social..social.,alt_Conf)) + 
  geom_smooth(aes(social..social.,alt_Conf, color = "green"), method = "lm") +  
  #geom_point(aes(social..social.,alt_Resp)) + 
  geom_smooth(aes(social..social.,alt_Resp, color = "blue"), method = "lm") +
  scale_color_discrete(name = "Attributed", labels = c("Dehumanization", "Conflictive", "Responsiveness")) +
  labs(title = "Social terms",x = "Proportion", y = "Partner attributions")

# Cognitive terms
D<-ggplot(Output) + 
  #geom_point(aes(cogproc..cognitive.processes.,alt_Dehum)) + 
  geom_smooth(aes(cogproc..cognitive.processes.,alt_Dehum, color = "red"), method = "lm") +
  #geom_point(aes(cogproc..cognitive.processes.,alt_Conf)) + 
  geom_smooth(aes(cogproc..cognitive.processes.,alt_Conf, color = "green"), method = "lm") +  
  #geom_point(aes(cogproc..cognitive.processes.,alt_Resp)) + 
  geom_smooth(aes(cogproc..cognitive.processes.,alt_Resp, color = "blue"), method = "lm") +
  scale_color_discrete(name = "Attributed", labels = c("Dehumanization", "Conflictive", "Responsiveness")) +
  labs(title = "Cognitive terms",x = "Proportion", y = "Partner attributions")


# Perceptual terms
E<-ggplot(Output) + 
  #geom_point(aes(percept..perceptual.processes.,alt_Dehum)) + 
  geom_smooth(aes(percept..perceptual.processes.,alt_Dehum, color = "red"), method = "lm") +
  #geom_point(aes(percept..perceptual.processes.,alt_Conf)) + 
  geom_smooth(aes(percept..perceptual.processes.,alt_Conf, color = "green"), method = "lm") +  
  #geom_point(aes(percept..perceptual.processes.,alt_Resp)) + 
  geom_smooth(aes(percept..perceptual.processes.,alt_Resp, color = "blue"), method = "lm") +
  scale_color_discrete(name = "Attributed", labels = c("Dehumanization", "Conflictive", "Responsiveness")) +
  labs(title = "Perceptual terms",x = "Proportion", y = "Partner attributions")

# Biological terms
F<-ggplot(Output) + 
  #geom_point(aes(bio..biological.processes.,alt_Dehum)) + 
  geom_smooth(aes(bio..biological.processes.,alt_Dehum, color = "red"), method = "lm") +
  #geom_point(aes(bio..biological.processes.,alt_Conf)) + 
  geom_smooth(aes(bio..biological.processes.,alt_Conf, color = "green"), method = "lm") +  
  #geom_point(aes(bio..biological.processes.,alt_Resp)) + 
  geom_smooth(aes(bio..biological.processes.,alt_Resp, color = "blue"), method = "lm") +
  scale_color_discrete(name = "Attributed", labels = c("Dehumanization", "Conflictive", "Responsiveness")) +
  labs(title = "Biological terms",x = "Proportion", y = "Partner attributions")

# Drive terms
G<-ggplot(Output) + 
  #geom_point(aes(drives..drives.,alt_Dehum)) + 
  geom_smooth(aes(drives..drives.,alt_Dehum, color = "red"), method = "lm") +
  #geom_point(aes(drives..drives.,alt_Conf)) + 
  geom_smooth(aes(drives..drives.,alt_Conf, color = "green"), method = "lm") +  
  #geom_point(aes(drives..drives.,alt_Resp)) + 
  geom_smooth(aes(drives..drives.,alt_Resp, color = "blue"), method = "lm") +
  scale_color_discrete(name = "Attributed", labels = c("Dehumanization", "Conflictive", "Responsiveness")) +
  labs(title = "Drive-related terms",x = "Proportion", y = "Partner attributions")

# Informal terms
H<-ggplot(Output) + 
  #geom_point(aes(informal..informal.language.,alt_Dehum)) + 
  geom_smooth(aes(informal..informal.language.,alt_Dehum, color = "red"), method = "lm") +
  #geom_point(aes(informal..informal.language.,alt_Conf)) + 
  geom_smooth(aes(informal..informal.language.,alt_Conf, color = "green"), method = "lm") +  
  #geom_point(aes(informal..informal.language.,alt_Resp)) + 
  geom_smooth(aes(informal..informal.language.,alt_Resp, color = "blue"), method = "lm") +
  scale_color_discrete(name = "Attributed", labels = c("Dehumanization", "Conflictive", "Responsiveness")) +
  labs(title = "Informal terms", x = "Proportion", y = "Partner attributions")

# Relative terms
I<-ggplot(Output) + 
  #geom_point(aes(relativ..relativity.,alt_Dehum)) + 
  geom_smooth(aes(relativ..relativity.,alt_Dehum, color = "red"), method = "lm") +
  #geom_point(aes(relativ..relativity.,alt_Conf)) + 
  geom_smooth(aes(relativ..relativity.,alt_Conf, color = "green"), method = "lm") +  
  #geom_point(aes(relativ..relativity.,alt_Resp)) + 
  geom_smooth(aes(relativ..relativity.,alt_Resp, color = "blue"), method = "lm") +
  scale_color_discrete(name = "Attributed", labels = c("Dehumanization", "Conflictive", "Responsiveness")) +
  labs(title = "Relative terms (space, time, movement)",
       x = "Proportion", y = "Partner attributions")


library(ggpubr)
ggarrange(A, B, C, D, E, F, G, H, I, legend = "bottom", common.legend = TRUE, nrow = 3, ncol = 3)

```
**Comments**: Note that Social terms, Biological words, Drive-related words -and to some extent Cognitive terms- describe similar patterns: the more frequent the use, the less likeable is the partner

## Stepwise Regressions
For each one of the three partner perception outcomes, I ran a 10-fold crossvalidated stepwise regression model (ML approach to evaluate the linear model with best fit over 10 simulations). As predictors, all sub-categories of words were introduced - except for function words were excluded from the analyses, since they were not giving consistent results and are hard to intepret. The three best models generated are presented in this table. Only a few word-types are significant predictors of all three predictors.

``` {r stepwise, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

## 10-fold Cross-validation
library(MASS)
resMatR = data.frame(Formula = vector(mode = "character", length = 10),
                    R_Squared = vector(mode = "numeric", length = 10),
                    r_test = vector(mode = "numeric", length = 10), stringsAsFactors = FALSE)

resMatC = data.frame(Formula = vector(mode = "character", length = 10),
                     R_Squared = vector(mode = "numeric", length = 10),
                     r_test = vector(mode = "numeric", length = 10), stringsAsFactors = FALSE)

resMatM = data.frame(Formula = vector(mode = "character", length = 10),
                     R_Squared = vector(mode = "numeric", length = 10),
                     r_test = vector(mode = "numeric", length = 10), stringsAsFactors = FALSE)

for (i in 1:10){
index<-sample(1:nrow(Output), ceiling(nrow(Output)*4/5))
Train<-Output[index,]
Test<- Output[-index,]


fullR<-lm(data=Train, alt_Resp ~ affect..affect..posemo..positive.emotions. + affect..affect..negemo..negative.emotions..anx..anx. + affect..affect..negemo..negative.emotions..anger..anger. + affect..affect..negemo..negative.emotions..sad..sad. + social..social..family..family. + social..social..friend..friends. + social..social..female..female. + social..social..male..male. + cogproc..cognitive.processes..insight..insight. + cogproc..cognitive.processes..cause..causal. + cogproc..cognitive.processes..discrep..discrepancies. + cogproc..cognitive.processes..tentat..tentative. + cogproc..cognitive.processes..certain..certainty. + cogproc..cognitive.processes..differ..differentiation. + percept..perceptual.processes..see..see. + percept..perceptual.processes..hear..hear. + percept..perceptual.processes..feel..feel. + bio..biological.processes..body..body. + bio..biological.processes..health..health. + bio..biological.processes..sexual..sexual. + bio..biological.processes..ingest..ingest. + drives..drives..affiliation..affiliation. + drives..drives..achieve..achievement. + drives..drives..power..power. + drives..drives..reward..reward. + drives..drives..risk..risk. + timeorient..time.orientation..focuspast..past.focus.+ timeorient..time.orientation..focuspresent..present.focus. +timeorient..time.orientation..focusfuture..future.focus.+ relativ..relativity..motion..motion. +relativ..relativity..space..space. + relativ..relativity..time..time. + persconc..personal.concerns..work..work. + persconc..personal.concerns..leisure..leisure. + persconc..personal.concerns..home..home. +persconc..personal.concerns..money..money. + persconc..personal.concerns..relig..religion. +persconc..personal.concerns..death..death. + informal..informal.language..swear..swear. + informal..informal.language..netspeak..netspeak. + informal..informal.language..assent..assent. + informal..informal.language..nonflu..nonfluencies. + informal..informal.language..filler..filler.words.)

fullC<-lm(data=Train, alt_Conf ~ affect..affect..posemo..positive.emotions. + affect..affect..negemo..negative.emotions..anx..anx. + affect..affect..negemo..negative.emotions..anger..anger. + affect..affect..negemo..negative.emotions..sad..sad. + social..social..family..family. + social..social..friend..friends. + social..social..female..female. + social..social..male..male. + cogproc..cognitive.processes..insight..insight. + cogproc..cognitive.processes..cause..causal. + cogproc..cognitive.processes..discrep..discrepancies. + cogproc..cognitive.processes..tentat..tentative. + cogproc..cognitive.processes..certain..certainty. + cogproc..cognitive.processes..differ..differentiation. + percept..perceptual.processes..see..see. + percept..perceptual.processes..hear..hear. + percept..perceptual.processes..feel..feel. + bio..biological.processes..body..body. + bio..biological.processes..health..health. + bio..biological.processes..sexual..sexual. + bio..biological.processes..ingest..ingest. + drives..drives..affiliation..affiliation. + drives..drives..achieve..achievement. + drives..drives..power..power. + drives..drives..reward..reward. + drives..drives..risk..risk. + timeorient..time.orientation..focuspast..past.focus.+ timeorient..time.orientation..focuspresent..present.focus. +timeorient..time.orientation..focusfuture..future.focus.+ relativ..relativity..motion..motion. +relativ..relativity..space..space. + relativ..relativity..time..time. + persconc..personal.concerns..work..work. + persconc..personal.concerns..leisure..leisure. + persconc..personal.concerns..home..home. +persconc..personal.concerns..money..money. + persconc..personal.concerns..relig..religion. +persconc..personal.concerns..death..death. + informal..informal.language..swear..swear. + informal..informal.language..netspeak..netspeak. + informal..informal.language..assent..assent. + informal..informal.language..nonflu..nonfluencies. + informal..informal.language..filler..filler.words.)

fullM<-lm(data=Train, alt_Dehum ~ affect..affect..posemo..positive.emotions. + affect..affect..negemo..negative.emotions..anx..anx. + affect..affect..negemo..negative.emotions..anger..anger. + affect..affect..negemo..negative.emotions..sad..sad. + social..social..family..family. + social..social..friend..friends. + social..social..female..female. + social..social..male..male. + cogproc..cognitive.processes..insight..insight. + cogproc..cognitive.processes..cause..causal. + cogproc..cognitive.processes..discrep..discrepancies. + cogproc..cognitive.processes..tentat..tentative. + cogproc..cognitive.processes..certain..certainty. + cogproc..cognitive.processes..differ..differentiation. + percept..perceptual.processes..see..see. + percept..perceptual.processes..hear..hear. + percept..perceptual.processes..feel..feel. + bio..biological.processes..body..body. + bio..biological.processes..health..health. + bio..biological.processes..sexual..sexual. + bio..biological.processes..ingest..ingest. + drives..drives..affiliation..affiliation. + drives..drives..achieve..achievement. + drives..drives..power..power. + drives..drives..reward..reward. + drives..drives..risk..risk. + timeorient..time.orientation..focuspast..past.focus.+ timeorient..time.orientation..focuspresent..present.focus. +timeorient..time.orientation..focusfuture..future.focus.+ relativ..relativity..motion..motion. +relativ..relativity..space..space. + relativ..relativity..time..time. + persconc..personal.concerns..work..work. + persconc..personal.concerns..leisure..leisure. + persconc..personal.concerns..home..home. +persconc..personal.concerns..money..money. + persconc..personal.concerns..relig..religion. +persconc..personal.concerns..death..death. + informal..informal.language..swear..swear. + informal..informal.language..netspeak..netspeak. + informal..informal.language..assent..assent. + informal..informal.language..nonflu..nonfluencies. + informal..informal.language..filler..filler.words.)


stepR<-stepAIC(fullR, direction = "both", trace = FALSE)
FmlaR<- stepR$call$formula
SumR<-stepR%>% summary()
R2R<-SumR$r.squared
r_testR<-cor(as.numeric(predict(stepR, newdata = Test)),Test$alt_Resp)

stepC<-stepAIC(fullC, direction = "both", trace = FALSE)
FmlaC<- stepC$call$formula
SumC<-stepC%>% summary()
R2C<-SumC$r.squared
r_testC<-cor(as.numeric(predict(stepC, newdata = Test)),Test$alt_Conf)



stepM<-stepAIC(fullM, direction = "both", trace = FALSE)
FmlaM<- stepM$call$formula
SumM<-stepM%>% summary()
R2M<-SumM$r.squared
r_testM<-cor(as.numeric(predict(stepM, newdata = Test)),Test$alt_Dehum)


resMatR[i,1]<-as.character(FmlaR[3])
resMatR[i,2]<-R2R
resMatR[i,3]<-r_testR

resMatC[i,1]<-as.character(FmlaC[3])
resMatC[i,2]<-R2C
resMatC[i,3]<-r_testC


resMatM[i,1]<-as.character(FmlaM[3])
resMatM[i,2]<-R2M
resMatM[i,3]<-r_testM

}

resMatC<-resMatC %>% 
  mutate(Product = sqrt(R_Squared^2+ r_test^2)* r_test^2/R_Squared) 
BestC<-resMatC[which(resMatC$Product ==max(resMatC$Product)),1]
resMatM<-resMatM %>% 
  mutate(Product = sqrt(R_Squared^2+ r_test^2)* r_test^2/R_Squared) 
BestM<-resMatC[which(resMatM$Product ==max(resMatM$Product)),1]
resMatR<-resMatR %>% 
  mutate(Product = sqrt(R_Squared^2+ r_test^2)* r_test^2/R_Squared) 
BestR<-resMatR[which(resMatR$Product ==max(resMatR$Product)),1]


## Running the best regressions ever
library(stargazer)
Reg1<-lm(data=Output, paste("alt_Resp", "~", BestR, sep = "")) 
Reg2<-lm(data=Output, paste("alt_Conf", "~", BestC, sep = ""))
Reg3<-lm(data=Output, paste("alt_Dehum", "~", BestM, sep = ""))

#Terms<-c("Positive Affect",  "Negative Affect: Sadness", "Negative Affect: Anxiety", "Negative Affect: Anger",,"Social words: Friends", "Social words: female",  "Cognitive: Insight","Cognitive: Causal terms", "Perception: Feel", "Biological terms: Ingest", "Drives: power","Cognitive: Tentative talk", "Perception: Hear", "Biological terms: Body", "Biological terms:Health","Time Focus: Present", "Relative: Motion terms", "Concerns: Home", "Concerns: Money", "Concerns:Death","Informal: Swear", "Drives: Affiliation", "Drives: Achievement", "Drives: Reward", "Time Focus: Past","Concerns: Religion", "Informal: Netspeak", "Informal: Assent", "Informal: filler words", "Informal:nonfluencies")

stargazer(Reg1, Reg2, Reg3,type = "html", out = "Test.html",dep.var.labels = c("Responsiveness","Conflict", "Mind"), dep.var.caption = "Attributes perceived by partner",initial.zero = FALSE,single.row = TRUE, header = TRUE, title = "Regressions: best models of words predicting partner perception",  digits = 2, model.numbers = FALSE, no.space = TRUE, align = TRUE, notes.align = "c", notes.append = FALSE)
```
